Age-related changes in plant growth and traits

### 2015-04-29 results_RAschedules.Rmd
Continuing to explore patterns of RA, RGR, growth, repro investment Strong correlations between shifts in growth vs. repro and height (within species) is particularly interesting - "cleaner" RA schedules against height than age or weight

source("scripts/summary_dataframes.R")
```
#RV curves and RA schedules, general patterns

@@

summarise_all_fits <- function(x) {
  tmp <- lapply(x, summarise_fit) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}
```

#RV curves
```{r, echo=FALSE,message=FALSE}
plot(ReproInv~FinalWeight, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

@@

#Reproductive Investment by Growth Investment
```{r, echo=FALSE,message=FALSE}
plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

yvar <- "ReproInv"
xvar <- "GrowthInv"

@@

#RA by Growth Investment
```{r, echo=FALSE,message=FALSE}
plot(RA~GrowthInv, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

yvar <- "RA"
xvar <- "GrowthInv"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

@@

#Reproductive Investment by scaled height 
For these calculations, height is scaled relative to max height. This should be a way to determine RSOM - RSOM would be the PropH at which Reproductive Investment begins.

```{r, echo=FALSE, message=FALSE}
plot((1+ReproInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot((1+ReproInv)~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "PropH"
xvar <- "ReproInv"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]]+1)))
results <- summarise_all_fits(lmfits)

@@

@@

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

@@

#Growth Investment versus proportion max H
This turns out to be one of the most interesting sets of graphs
For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH
For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)
Quite interesting, there is a distinctly negative relationship for GRBU
For many of the species with a good relationship, it seems that there are two breakpoints in the curve - wondering what these mean with respect to reproductive onset and RA

```{r, echo=FALSE, message=FALSE}
plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(GrowthInv~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "GrowthInv"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)

@@

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])+(x[[x2var]])))
results <- summarise_all_fits(lmfits)

@@

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="BOLE"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="GRBU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="GRSP"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PELA"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="HATE"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="BAER"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PEPU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="EPMI"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="LEES"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PHPH"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PUTU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="HEPU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PILI"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="COER"))
summary(mod)
anova(mod)
```{r, echo=FALSE, message=FALSE}
plot((RGR~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "RGR"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)
  abline(lmfits[[spp]])
}
```

#Plotting RGR and RA vs. proportion maxH and simply RA vs RGR

```{r, echo=FALSE, message=FALSE}
plot(RGR~PropH,data=subset(SummaryInd, species=="BAER"),pch=16, col="black")
points((5*RA)~PropH,data=subset(SummaryInd, species=="BAER"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="HATE"),pch=16, col="black")
points((10*RA)~PropH,data=subset(SummaryInd, species=="HATE"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="EPMI"),pch=16, col="black")
points((5*RA)~PropH,data=subset(SummaryInd, species=="EPMI"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="PEPU"),pch=16, col="black")
points((3*RA)~PropH,data=subset(SummaryInd, species=="PEPU"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="BOLE"),pch=16, col="black")
points((3*RA)~PropH,data=subset(SummaryInd, species=="BOLE"),pch=16, col="red")

plot((1/RGR)~(RA),SummaryInd,log="y",col=col.spp[as.factor(species)],pch=16)
plot((RGR)~(RA),data=subset(SummaryInd,species=="BOLE"),log="y",col=col.spp[as.factor(species)],pch=16)
mod <- lm(RA~log(RGR),data=subset(SummaryInd,species=="BOLE"))
summary(mod)

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)
  abline(lmfits[[spp]])
}

>>>>

source("scripts/summary_dataframes.R")
```
#RV curves and RA schedules, general patterns
- RA best plotted against height for many species - much clearer pattern than against weight or age - this seems to support Daniel's suspicion that deadwood shouldn't be included in the "weight" of the plant
- A number of species show an abrupt decrease in RGR (or tapering of growth investment) at the height where reproduction begins. This is evidence of the growth-reproduction trade-off
- RV curves are mostly quite pretty, but not necessarily very meaningful

@@

summarise_all_fits <- function(x) {
  tmp <- lapply(x, summarise_fit) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}

summarise_fit_2var <- function(x) {
  data.frame(
    select(glance(x), r.squared, p.value),
    n= length(resid(x)),
    intercept = coef(x)[1],
    coef_var1 = coef(x)[2],
    coef_var2 = coef(x)[3],
    coef_var1var2 = coef(x)[4],
    SS_var1 = anova(x)[1,2],
    SS_var2 = anova(x)[2,2],
    SS_var1var2 =anova(x)[3,2]
      )
}

summarise_all_fits_2var <- function(x) {
  tmp <- lapply(x, summarise_fit_2var) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}
```

#RV curves
These are mostly reasonably nice - of course need to fit quadratic curve to these and haven't figured out how to do it correctly

```{r, echo=FALSE,message=FALSE}
plot(ReproInv~FinalWeight, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

#RA schedules (vs. propH)
- these curves are particularly good for a number of species such as EPMI, COER, PELA
- they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing propH

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

@@

#Reproductive Investment by Growth Investment
Overall, these are not a strong set of results, but HATE shows a very strong relationship that shows reproductive investment (not growth investment) asymptoting
Interestingly, PHPH, which is generally a complete scatter plot, has one of the strongest correlations between these variables, indicating that indeed most measures of "size" for this multi-stemmed plant aren't very meaningful and it should be analyzed differently.

Note that the analyses are just being done on reproducing individuals at the moment.
```{r, echo=FALSE,message=FALSE}
plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

yvar <- "GrowthInv"
xvar <- "ReproInv"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

@@

#RA by Growth Investment
Across all species, high RA = low growth investment. This pattern exists mostly because of shifts in species from high reproducers to high growers - i.e. BOLE in one corner, and BAER & HATE in another.
For analyses within individual species
```{r, echo=FALSE,message=FALSE}
plot(RA~GrowthInv, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

plot(GrowthInv~RA, data=subset(SummaryInd,RA>0), log="y", col=col.spp[as.factor(species)],pch=16)
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
mod <- lm(log(GrowthInv)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
summary(mod)
plot(mod)

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

@@

#RA vs RGR - 
similar to the plots of RA vs Growth Investment, but relationships stronger. For these plots, all but one species (PEPU) have a significantly negative slope
the results are more of less the same regardless of whether one includes or excluded individuals where RA=0
```{r, echo=FALSE,message=FALSE}
plot(RA~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(RA~RGR, SummaryInd, log="x", col=col.age[as.factor(age)],pch=16)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

plot(RGR~RA, data=subset(SummaryInd,RA>0), log="xy", col=col.spp[as.factor(species)],pch=16)
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
mod <- lm(log(GrowthInv)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
summary(mod)
plot(mod)

yvar <- "RGR"
xvar <- "RA"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

@@

#Reproductive Investment by scaled height 
For these calculations, height is scaled relative to max height. This should be a way to determine RSOM - RSOM would be the PropH at which Reproductive Investment begins.
For species such as BOLE which begin reproduction so young, data could be included that have pre-reproductive heights from mid-year censuses of "babies"

```{r, echo=FALSE, message=FALSE}
plot((RA~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot((RA)~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

@@

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

@@

@@

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))*asin(sqrt(x[[x2var]]))))
results <- summarise_all_fits_2var(lmfits)

@@

### 2015-04-29 results_growth.Rmd
Continuing to explore patterns of RA, RGR, growth, repro investment Strong correlations between shifts in growth vs. repro and height (within species) is particularly interesting - "cleaner" RA schedules against height than age or weight

source("scripts/summary_dataframes.R")
```
#Growth data, general patterns

@@

@@

```

>>>>

source("scripts/summary_dataframes.R")
```
#Growth data, general patterns
- proportion of maxH matters more for some species than others. 
1. The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  
2. The lower-growing species are more variable, with "prop maxH mattering more for some than others"

- For almost all species there is a strong negative relationship between RGR and RA - indeed, more reproduction = less growth  
1. Meanwhile there is the strong positive relationship between growth investment and reproductive investment, because bigger plants grow and reproduce more.  
2. It is good to have a big enough data set to capture both trends - and to capture them consistently across many species

- Many plants have a clear upturn in RA and corresponding downturn in RGR at a specific prop maxH  
1. e.g. see EPMI for distinct pattern

@@

#Growth Investment versus proportion max H
This turns out to be one of the most interesting sets of graphs
For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH
For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)
Quite interesting, there is a distinctly negative relationship for GRBU
For many of the species with a good relationship, it seems that there are two breakpoints in the curve - wondering what these mean with respect to reproductive onset and RA

```{r, echo=FALSE, message=FALSE}
plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(GrowthInv~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "GrowthInv"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#A series of models by species showing the relative influence "RA" and "proportion of max H" have on growth investment.
- These models show that the relative contribution of these two factors differs across species, with the 4 canopy species (PELA, HATE, BAER, PEPU) more influenced by height and other many of the species more influenced by RA.  
- This reflects in part, the fact that many of the "canopy" species show lots of year-to-year variation in reproductive output   
- Across the board, most species have quite high R^2 values   
- Model with RA, PropH, and species has R^2 = 0.8231

```{r, echo=FALSE, message=FALSE}
mod <- lm(log(GrowthInv)~asin(sqrt(PropH))*asin(sqrt(RA))*species,data=subset(SummaryInd))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="BAER"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="BOLE"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="COER"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="EPMI"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="GRBU"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="GRSP"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="HATE"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="HEPU"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="LEES"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="PELA"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="PEPU"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="PHPH"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="PILI"))
summary(mod)
anova(mod)
plot(mod)

mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="PUTU"))
summary(mod)
anova(mod)
plot(mod)
```

#Proportion max H by RGR
Excepting some outliers, RGR declines with increasing height  
Except in a few species there is little pattern - HEPU, PILI  
The species with a room correlation are mostly shorter ones that are presumably often broken off 
These are continued ways to look at the question of how important is height (relative to the species maxH) in understanding its growth and reproduction

```{r, echo=FALSE, message=FALSE}
plot((RGR~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "RGR"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)
  abline(lmfits[[spp]])
}
```

#Plots of Growth Inv versus weight - showing that slope continues to be 1:1, but intercept decreases with time because more standing biomass
```{r, echo=FALSE, message=FALSE}
plot((GrowthInv~FinalWeight), SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
abline(0,1,lwd=2)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(GrowthInv~FinalWeight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
abline(0,1,lwd=2)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
```

#Plotting RA vs RGR
Higher RA = lower RGR, for all species except PEPU  
1. PEPU an exception because so few individuals reproducing and those that are reproducing have intermediate RGR - neither the young plants nor the older plants just hanging on
2. PELA doesn't have a relationship either, because so few reproducing individuals. But if the many individuals with RA=0 added back in, strong negative relationship for PELA

@@

plot(RGR~RA,data=subset(SummaryInd,RA>0&RGR>.04),log="y",col=col.spp[as.factor(species)],pch=16)
mod <-lm(log(RGR)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&RGR>.04))
summary(mod)
plot(mod)

yvar <- "RGR"
xvar <- "RA"

data <- subset(SummaryInd, RA>0&RGR>.04)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```
